A Formal Model of Checked C

### 2023-01-14 sandp23/formal.tex
[review] rewrite dependnt FP

\myparagraph{Dependent Function Pointers}
Given a function pointer type ($\tptr{\tfun{\overline{x}}{\overline{\tau}}{\tau}}{\xi}$)
from a type-check for $e$ and the types $\overline{\tau'}$ from the argument type checks for $\overline{e}$,
we confirm that each of $\overline{\tau'}$ is
a subtype of the corresponding one in $\overline{\tau}[\overline{e'} / \overline{x}]$ 
in rule \textsc{T-Fun} (\Cref{fig:type-system-1}),
which replaces possible integer bound variables $\overline{x}$ with bound expressions $\overline{e'}$.
The final result type is the defined target type $\tau$ appearing in the function pointer type
also with such replacement, written as $\tau[\overline{e'} / \overline{x}]$.
Consider the \code{process_req2} function in
Fig.~\ref{lst:final}; its parameter type for \code{msg} 
depends on \code{m_1}. The \textsc{T-Fun} rule will substitute 
\code{n} with the argument at a call-site.
\ignore{
The semantics manages variable scopes using the special $\erettext$
form. \textsc{S-Let} evaluates to a configuration whose expression is
$\ret{x}{\evalue{n}{\tau}}{e})$. We keep $\varphi$ unchanged
and remember $x$ and its new value $\evalue{n}{\tau}$
in $e$'s scope that is defined by the $\erettext$ operation.
Every time when evaluation proceeds on $e$ (rule \textsc{S-RetCon}),
we install the stack value $\evalue{n}{\tau}$ for $x$ in $\varphi$ for the current scope.
After one-step evaluation is completed, 
we store $x$'s change in the result $\erettext$ operation $\ret{x}{\varphi'(x)}{e'})$,
and restore $x$'s outer score value $\varphi(x)$ in $\varphi'$. 
This procedure continues until $e'$ becomes a literal
$n\!:\!\tau$, in which case \textsc{S-RetEnd} removes the $\kw{ret}$ frame and returns
the literal. 
}

>>>>

\myparagraph{Dependent Function Pointers} %
The rule \textsc{T-Fun} (\Cref{fig:type-system-1}) states the type judgement for
dependent function pointer application where we represent the result of
replacing all integer bound variables $\overline{x}$ in the type \(\tau\) with
with bound expressions $\overline{e'}$ by $\tau[\overline{e'} / \overline{x}]$
and write $\overline{\tau}[\overline{e'} / \overline{x}]$ to lift the
substitution to every type \(\overline{\tau}\).
% 
Given an expression $e$ of function pointer type
($\tptr{\tfun{\overline{x}}{\overline{\tau}}{\tau}}{\xi}$) and arguments
$\overline{e}$ of types $\overline{\tau'}$,
% 
the result of the application will
be of type $\tau[\overline{e'} / \overline{x}]$ 
% 
if for each pair of \(\tau'\) and \(\tau''\) in \(\overline{\tau'}\) and
$\overline{\tau}[\overline{e'} / \overline{x}]$, \(\tau'\) is a subtype of
\(\tau''\).
% 
\mz{I rewrote the sentences above.}
% 
Consider the \code{process_req2} function in
Fig.~\ref{lst:final}; its parameter type for \code{msg} 
depends on \code{m_1}. The \textsc{T-Fun} rule will
\mzu{substitute \code{n} with the argument}
\mz{\code{n} seems unbound here.}
at a call-site.
\ignore{
The semantics manages variable scopes using the special $\erettext$
form. \textsc{S-Let} evaluates to a configuration whose expression is
$\ret{x}{\evalue{n}{\tau}}{e})$. We keep $\varphi$ unchanged
and remember $x$ and its new value $\evalue{n}{\tau}$
in $e$'s scope that is defined by the $\erettext$ operation.
Every time when evaluation proceeds on $e$ (rule \textsc{S-RetCon}),
we install the stack value $\evalue{n}{\tau}$ for $x$ in $\varphi$ for the current scope.
After one-step evaluation is completed, 
we store $x$'s change in the result $\erettext$ operation $\ret{x}{\varphi'(x)}{e'})$,
and restore $x$'s outer score value $\varphi(x)$ in $\varphi'$. 
This procedure continues until $e'$ becomes a literal
$n\!:\!\tau$, in which case \textsc{S-RetEnd} removes the $\kw{ret}$ frame and returns
the literal. 
}
